Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-10 IUI2021/paper.tex
...

% \documentclass[manuscript,anonymous,review]{acmart}
\documentclass[manuscript,screen,review]{acmart}

@@

The help system of MacOS (Catalina v10.15.5) cannot tell us how to remove a file.

\begin{figure}[H]
  %\centering
  % \includegraphics[width=7cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/eaa80e41ddc3d3620fae133007274573.png}
  % \includegraphics[width=7cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \par
  (a) Searching ``remove files'' \hspace{3cm} (b) Searching ``Set clock''
  \caption{Asking the help application on Mac how to remove a file.}
  %\Description{Mac Mac}
\end{figure}

Using the same help application, 
a user can find how to set the system clock of the computer,
but the user has to know that
``setting the clock'' and ``changing date'' means the same thing.

@@

We can get this kind of information fairly easily using search systems on the net,
so many people prefer getting information using search engines rather than
using help systems provided by manufacturers.

@@

On the other hand,
finding a less popular information is rather difficult,
because not enough documents related to the topic is found on the net.
%
If there is only one document on the net
that describes the \texttt{console} feature of a minor system \texttt{xxxxx},
people cannot find the document using a similar keyword \texttt{dashboard}
since the document does not contain the word \texttt{dashboard}.

@@

FAQs (frequently asked questions) provided by service providers are
usually not considered useful
because the terms used by the people on the service are usually
different from the keywords that user can imagine.

@@

Even finding the users' old documents can be sometimes difficult,
because people might use different keywords for the same thing case by case.
He might try to find a file related to ``IUI'' and fail, because he used
the term ``intelligent user interface'' for the file name.
%
Various techniques have been proposed to solve this vocabulary problem\cite{Furnas},
but not very successful enough.

@@

Finding documents are even more difficult when
the user's mother language is different from the language used in the document.
When a user wants to find how to ``delete a file'' but the
manual of the system is written in French,
he has to translate the term ``delete'' and ``file'' into French
before the search.
Non-English speakers are always having trouble
translating the word in their brain into English words
before searching information, because important information are
usually provided in English.

@@

The vocabulary problem and the translation problem can sometimes be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file mean the same thing,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
Techniques like this are called ``\textit{Query expansion}''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Query\_expansion}
},
and simple query expansion is possible if a good thesaurus is available.

@@

However, query expansion techniques do not work for finding a document for vague topics.
For example, if you want to find a document that describes ``how to write a good paper'',
you will have little chance finding a document related to the topic.
Maybe it would be better to use keywords like ``how to persuade reviewers''.
However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
unless the expander knows the contents.

@@

Similarly, 
when we want to find a library function of a programming language,
query expansion sometimes does not work.
For example, when we want to write a poker game program and
want to write a program that select five cards from 52 cards,
what library should we use?
you want to selet randomly two items from an array in Ruby,
you can use the \texttt{sample()} method.
However, ``randomly selecting items'' and \texttt{sample} are so different, it is very hard for users to
find the method unless the manual contains words like ``randomly select''.

% 「配列からランダムに要素をふたつ取得」 = `a.sample(2)`
%    `sample`という単語はなかなか出てこないのではないか
%    pick upとかselectとかchooseとか言ってしまいそう

It is even more difficult if the user wants to find information that is not easily described with keywords.
When a user wants to know the meaning of an icon on the desktop, he might think
``What is the symbol with curved lines and a circle
\includegraphics[width=6mm,bb=-40 30 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
at the top of my Mac display?'',
but he cannot finding the information using these keywords in his brain.
(folding fan, two black 90-degree arcs above a black circle)

@@

@@

To solve the vocabulary problem and the translation problem,
we propose the combination of three techniques described below.

We call the combination of these techniques as ``document expansion''.

@@

  When we want to provide a (flexible?) manual that describes how to delete a file,
  we expand the original document by
  providing REs like \verb*(delete|remove) (a file|data)*
  and generating all the texts that match the REs.
  In this case, we can epand this RE into
  \verb|delete a file|,
  \verb|delete data|,
  \verb|remove a file|, and
  \verb|remove data|,
  and use all these strings for the search.
  Users can find this document by using various query keywords like
  \verb|delete|, \verb|remove|, etc.
  We can add REs in other languages
  like \verb*(ファイル|データ)を(消す|(消去|削除)する)*.
  A Japanese user can use a phrase like ``ファイルを消去する'' to find the manual page.

@@

  People frequently make spelling errors,
  and approximate pattern matching algorithms
  work effectively for almost all search activities.
  Using the {\ES} algorithm, all the expressions are expanded,
  and simple approximate pattern matching algorithms work effectively.
  For example, a query like ``del dta'' will work for
  finding a document that describes how to ``delete data''.

@@

  One of the big reasons why we fail to find a document is that
  the user's search keyword does not exist in the document.
  If a user can expand the target documents by
  providing RE entries for {\ES},
  other users can use {\ES} for finding the documents.
  %
  This strategy is similar to creating an external index or
  writing a hands-on document for an existing document,
  but adding {\ES} entries is much easier and more flexible than
  authoring a document from scratch.

@@

@@

In this section, we describe how
document expansion strategy based on {\ES} works in various environments.

@@

Unix command line tools usually have many options and features that are difficult to
understand and remember.
Many programmers are recently using the git version control system,
but the concept of git is difficult, and
the command line options are extremely complicated.
The total number of git manuals on unix is xxxxx lines.

We created the {\HL} system using {\ES}, so that git users can easily
remember command options and use it without perfectly remembering the git commands.

We implemented the {\HL} system
with which a user can translate his vague intention in various languages
into a complete {\GIT} command
using the {\ES} framework.

@@

We assume that the user uses \tt{bash} for his software
development activities.
% 
When a user wants to compare the latest \stt{README.md} file
with the same file from 2 versions before,
he might try to use {\GIT} with an option
``{\smallfont\verb|HEAD^^|}''
for specifying the old version.

\begin{figure}[h]
  \vbox{
    \begin{verbatim}
      $ git diff HEAD^^ README.md
      $
    \end{verbatim}
  }
  \caption{Invoking \stt{git diff}.}
  \label{gitdiff}
\end{figure}

However, nothing happens here because
\verb|HEAD^^|
specifies a file included in the older commit,
and the command in figure \ref{gitdiff} only compares the
\stt{README.md} with the file included in an old commit, where
\stt{README.md} might not have changed since then.

@@

\begin{figure}[h]
  \includegraphics[width=9cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
  \caption{Invoking {\HL} after typing \stt{git read 2}.}
  \label{example1}
\end{figure}

Here, various candidate entries with descriptions and command strings are listed,
just like text input support systems for non-English languages.
One of the entries says
``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}'',
and if the user thinks that's what he wants to do,
he can select the entry by typing arrow keys and the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like \sqsf{2 days ago} is also shown in the candidate list
of Figure \ref{example1}.
This means that the user can use the same string \sqtt{git RE 2}
for getting the information of \stt{README.md} file of the day before yesterday.
The generated argument
``{\smallfont\verb|@{2 days ago}|}'',
may not be familiar to most {\GIT} users,
but users can perform this task only by giving \sqtt{RE} and \sqtt{2}
without knowing the correct syntax of this option.

When the user types the shortcut key
after typing \sqtt{git sh reed 3},
approximate pattern matching is automatically performed, and
entries related to \stt{README.md} file are listed because
\sqtt{reed} matches \sqtt{README.md} with one error.

\begin{figure}[h]
  \includegraphics[width=9cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
  \caption{Invoking {\HL} after typing \stt{git sh reed 3}.}
  \label{example2}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
  \caption{Invoking {\HL} in Japanese environment.}
  \label{example3}
\end{figure}

If the user wants to know more about the command line,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{../../GitHelp/paper/figures/info-xxl.png}}
button and see the Wiki page shown in Figure \ref{scrapboxpage}.
The user can edit the page if he wants to add information or finds an error.
In this page, description part is preceded by a ``\texttt{\$}'' symbol and
the command part is preceded by ``\texttt{\%}''.

\begin{figure}[t]
  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{../../GitHelp/paper/figures/scrapbox3.png}}
  \caption{A {\SB} page for \tt{git diff}.}
  \label{scrapboxpage}
\end{figure}

\subsection{OmniSearch}

OmniSearch is an implementation of {\ES} that runs on Chrome browser.
The URL window on Chrome is called omnibox,

@@

Figure \ref{paypayhf} shows an example {\HF} page that supports finding FAQs
for ``PayPay Free Market'' run by Yahoo! Japan\footnote{
  \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
}.

% We provide the description on the Scrapbox wiki service,

\begin{figure}[H]
  \centering
  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
  \caption{PayPay Freemarket}
  \label{paypayhf}
  \Description{PayPay}
\end{figure}

ものすごく問いあわせが減った

@@

%\bibliographystyle{SIGCHI-Reference-Format}
%\bibliography{paper}

>>>>

\documentclass[manuscript,anonymous,review]{acmart}
% \documentclass[manuscript,screen,review]{acmart}

@@

The standard help system on MacOS (Catalina v10.15.5)
cannot tell the user how to remove a file (Figure \ref{machelp}(a)).
%
It can tell the user how to ``set the clock'', but
the user has to know that
``setting the clock'' and ``changing date'' means the same thing (Figure \ref{machelp}(b)).

\begin{figure}[H]
  %\centering
  % \includegraphics[width=7cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/eaa80e41ddc3d3620fae133007274573.png}
  % \includegraphics[width=7cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \par
  (a) Searching ``remove files'' \hspace{3cm} (b) Searching ``Set clock''
  \caption{Using the standard help application on Mac.}
  \label{machelp}
  %\Description{Mac Mac}
\end{figure}

@@

We can get this kind of information fairly easily using Google and other search engines on the net,
so many people prefer getting information on the net rather than
using help systems provided by manufacturers.

@@

On the other hand,
finding less popular information is more difficult,
because not enough documents related to the topic exist on the net.
%
If there is only one document on the net
that describes the \qtt{console} feature of a relatively minor system like \tt{Heroku},
people cannot find the document using a similar keyword \qtt{dashboard}
since the documents from \tt{Heroku} does not contain the word \qtt{dashboard}.

@@

FAQs (frequently asked questions) by manufacturers and service providers are
usually not considered useful
because the words used in the documents are
often different from the keywords that user can imagine.

@@

Even finding the users' old memos can be sometimes difficult,
because people might use different keywords for the same thing case by case.
He might try to find a file related to ``IUI'' and fail, because he used
the term ``intelligent user interface'' for the file name.
%
Various techniques have been proposed to solve this vocabulary problem\cite{Furnas:1987:VPH:32206.32212},
but not very successful enough.

@@

Finding documents are even more difficult when
the user's mother language is different from the language used in the document.
When a user wants to find how to ``delete a file'' but the
manual of the system is written in French,
he has to \textit{translate} the term ``delete'' and ``file'' into French
before the search.
Non-English speakers are always having trouble
translating the word in their brain into English words
before searching information, because important information are
usually provided in English.

@@

The vocabulary problem and the translation problem can partially be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file mean the same thing,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
Techniques like this are called ``\textit{Query expansion}''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Query\_expansion}
},
and simple query expansion is effective if a good thesaurus is available.

@@

However, query expansion techniques do not work for finding a document for vague topics.
For example, if you want to find a document that describes ``how to write a good paper'',
you will have little chance finding a document related to the topic.
Maybe it would be better to use keywords like ``how to persuade reviewers''.
However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
unless the expander understands the intension of the user.

@@

% ライブラリ関数 (やめる)
% 「配列からランダムに要素をふたつ取得」 = `a.sample(2)`
%    `sample`という単語はなかなか出てこないのではないか
%    pick upとかselectとかchooseとか言ってしまいそう

% Similarly, 
% when we want to find a library function of a programming language,
% query expansion sometimes does not work.
% For example, when we want to write a poker game program and
% want to write a program that select five cards from 52 cards,
% what library should we use?
% you want to selet randomly two items from an array in Ruby,
% you can use the \texttt{sample()} method.
% However, ``randomly selecting items'' and \texttt{sample} are so different, it is very hard for users to
% find the method unless the manual contains words like ``randomly select''.

@@

It is even more difficult if the user wants to find information that is not easily described with keywords.
When a user wants to know the meaning of an icon on the computer desktop, he might want to say
``What is the symbol with curved lines and a circle
\includegraphics[width=6mm,bb=-40 30 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
at the top of my Mac display?'',
but he cannot find the information using such keywords in his brain.
% (folding fan, two black 90-degree arcs above a black circle)

@@

To solve the vocabulary problem and the translation problem,
we propose the combination of three techniques described below.
%
We call the combination of these techniques as ``\textit{document expansion}''.

@@

  When we want to publish a easy-to-find manual that describes how to delete a file,
  we expand the original document by
  providing REs like \qtt{(delete|remove) (a file|data)}
  and generating all the texts that match the REs.
  In this case, we can epand this RE into
  \qtt{delete a file},
  \qtt{delete data},
  \qtt{remove a file}, and
  \qtt{remove data},
  and use all these strings for the search.
  Users can find this document by using various query keywords like
  \qtt{delete}, \qtt{remove}, etc.
  We can add REs in other languages
  like \qtt{(ファイル|データ)を(消す|(消去|削除)する)}.
  A Japanese user can use a phrase like ``ファイルを消去する'' to find the manual page.

@@

  Since people frequently make spelling errors,
  approximate pattern matching algorithms
  work effectively for almost all search activities.
  After getting all the expresssions expanded by the {\ES} algorithm,
  simple approximate pattern matching algorithms work effectively.
  For example, a query string like \qtt{del dta} will work for
  finding a document that describes how to ``delete data''.

@@

  One of the big reasons why we fail to find a document is that
  the user's search keyword does not exist in the document.
  If a user can expand the target documents by
  providing RE entries for {\ES} and share them,
  other users can use {\ES} for finding the documents.
  %
  This strategy is similar to creating an external index or
  writing a hands-on document for an existing document,
  but adding {\ES} entries is much easier and more flexible than
  authoring a document from scratch.

@@

In the next section, we describe how
document expansion strategy based on {\ES} works in various environments.

@@

@@

Unix command line tools usually have many options and features that are difficult to
understand and remember.
For example, many programmers are recently using a version controll system
``git''\footnote{
  \ssf{https:{\slash}{\slash}git-scm.com{\slash}}
},
but the concept of git is difficult and the command line options are extremely complicated.
The total number of git manuals pages is bigger than 70,000.

To solve the difficulty of using commands,
we created the {\HL} system using {\ES}, so that users of git and other complicated systems can
easily remember command options and use it without remembering the details of the commands.

We implemented the {\HL} system
with which a user can translate his vague intention in various languages
into a complete command line using the {\ES} framework.

@@

We assume that the user uses \tt{bash} for his software development activities.
% 
When a user wants to compare the latest \sqtt{README.md} file
with the same file from 2 versions before,
he might try to use {\GIT} with an option
``{\smallfont\verb|HEAD^^|}''
for specifying the old version.

% \begin{figure}[h]
%   \vbox{
%     \begin{verbatim}
%       $ git diff HEAD^^ README.md
%       $
%     \end{verbatim}
%   }
%   \caption{Invoking \stt{git diff}.}
%   \label{gitdiff}
% \end{figure}

\begin{quote}
\begin{verbatim}
$ git diff HEAD^^ README.md
$
\end{verbatim}
\end{quote}

However, nothing happens here because
\verb|HEAD^^|
specifies a file included in the older commit,
and the command compares the
\sqtt{README.md} with the file included in an old commit, where
\sqtt{README.md} might not have changed since then.

@@

\begin{figure}[H]
  \includegraphics[width=8cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
  \caption{Invoking {\HL} after typing \sqtt{git read 2}.}
  \label{example1}
\end{figure}

Here, various candidate entries with descriptions and command strings are listed,
just like text input support systems for non-English languages.
One of the entries says
``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}'',
and if the user thinks that's what he wants to do,
he can select the entry by typing arrow keys.
After typing the enter key for confirmation,
the user's input string is replaced by the right command string
that satisfies the user's need.

A description like \sqsf{2 days ago} is also shown in the candidate list
of Figure \ref{example1}.
This means that the user can use the same string \sqtt{git RE 2}
for getting the information of \sqtt{README.md} file of the day before yesterday.
The generated argument
``{\smallfont\verb|@{2 days ago}|}'',
may not be familiar to most {\GIT} users\footnote{
  The authors asked more than 10 experienced git users if they know that option,
  but nobody knew it.
},
but users can perform this task only by giving \sqtt{RE} and \sqtt{2}
without knowing the correct syntax of this option.

When the user types the shortcut key
after typing \sqtt{git sh reed 3},
approximate pattern matching is automatically performed, and
entries related to \sqtt{README.md} file are listed because
\sqtt{reed} matches \sqtt{README.md} with one error.

\begin{figure}[H]
  \includegraphics[width=8cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
  \caption{Invoking {\HL} after typing \stt{git sh reed 3}.}
  \label{example2}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=8cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
  \caption{Invoking {\HL} in Japanese environment.}
  \label{example3}
\end{figure}

If the user wants to know more about the command line,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{../../GitHelp/paper/figures/info-xxl.png}}
button and see the wiki page\footnote{
  A wiki system {\SB} (\ssf{https:{\slash}{\slash}Scrapbox.io{\slash}product{\slash}}) is used for the data sharing.
} shown in Figure \ref{scrapboxpage}.
The user can edit the page if he wants to add information or finds an error.
In this page, description part is preceded by a ``\texttt{\$}'' symbol and
the command part is preceded by ``\texttt{\%}''.

\begin{figure}[H]
  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{../../GitHelp/paper/figures/scrapbox3.png}}
  \caption{A {\SB} page for \tt{git diff}.}
  \label{scrapboxpage}
\end{figure}

Since the REs for expanding git manuals are written on wiki pages,
any members of the wiki project can edit the data and share it among other users.

% \subsection{OmniSearch}
% 
% OmniSearch is an implementation of {\ES} that runs on Chrome browser.
% The URL window on Chrome is called omnibox,

@@

Figure \ref{paypayhf} shows an example {\HF} page that supports finding FAQs
for ``PayPay Free Market'' run by Yahoo! Japan\footnote{
  \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
} and ``Siroca'', a consumer electronics company.

\begin{figure}[H]
  \centering
  % \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
  \includegraphics[width=7cm,bb=0 0 1982 1536]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
  \includegraphics[width=7cm,bb=0 0 1672 1472]{figures/6b491f2701af7193030e332686733568.png}
  \caption{PayPay Freemarket}
  \label{paypayhf}
  %\Description{PayPay}
\end{figure}

After the introduction of ExpandSearch-based FAQ services,
the number of phone calls to the customer support center of these companies have
dramatically reduced, as much as 60\%.
%
The ``hit rate'' at which users could find the information they need was 98\%.

@@

\newpage

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}
